Sustainable computational science:\\ the ReScience initiative

### 2017-07-13 draft.tex
Abstract rewrite

\twocolumn[
  \maketitle
  \vspace{5mm}
  \noindent
  \textbf{Abstract.}
  Computer science offers a large set of tools for prototyping, writing,
  running, testing, validating, sharing and replicating results, however computational
  science lags behind.
  In the best case, authors may provide their source code as a compressed archive and they may feel confident their research
  is replicable. But this is not exactly true. Buckheit \& Donoho 1995
  proposed more than 2 decades ago that, an article about computational results is
  advertising, not scholarship. The actual scholarship is the full software
  environment, code, and data that produced the result. The computational part
  in computational sciences implies the use of computers, operating systems,
  tools, frameworks, libraries, and data. This leads to a large number of
  combinations thereof (taking into account the version for each component) that the
  chances of having the exact same configuration as one of your colleagues are
  practically zero. This has consequences for computational
  approaches in order to make sure that computational research can be faithfully replicated.
  %
  ReScience is a peer-reviewed journal that targets computational research and
  encourages the explicit replication of already published research, promoting
  new and open-source implementations in order to ensure that the original
  research is reproducible. To achieve this goal, the whole publishing chain is
  radically different from other traditional scientific journals. ReScience
  resides on GitHub where each new implementation of a computational study is
  made available together with comments, explanations, and software tests. Each
  submission takes the form of a ``pull request'' that is publicly reviewed and
  tested in order to guarantee re-usability. ReScience is
  open and collaborative by design: everything can be modified.\\
  % \begin{small}
  % \vspace{10mm}

  \textbf{Keywords:} Open Science, Computational Science,
                     Reproducibility, Replicability, Journal, Publication
  %\end{small}
  %\vspace{10mm}
  \vfill
]

>>>>

\twocolumn[
  \maketitle
  \vspace{5mm}
  \noindent
  \textbf{Abstract.}
  %
  Computer science offers a large set of tools for prototyping, writing,
  running, testing, validating, sharing and replicating results, however
  computational science lags behind.  In the best case, authors may provide
  their source code as a compressed archive and they may feel confident their
  research is reproducible. But this is not exactly true. James Buckheit and
  David Donoho proposed more than 2 decades ago that an article about
  computational results is advertising, not scholarship. The actual scholarship
  is the full software environment, code, and data that produced the
  result. This implies new workflows, in particular in peer-reviews. Existing
  journals have been slow to adapt: source codes are rarely requested, hardly
  ever actually executed to check that they produce the results advertised in
  the article.
  %
  ReScience is a peer-reviewed journal that targets computational research and
  encourages the explicit replication of already published research, promoting
  new and open-source implementations in order to ensure that the original
  research can be replicated from its description. To achieve this goal, the
  whole publishing chain is radically different from other traditional
  scientific journals. ReScience resides on GitHub where each new
  implementation of a computational study is made available together with
  comments, explanations, and software tests.\\

  \textbf{Keywords:} Open Science, Computational Science,
                     Reproducibility, Replicability, Journal, Publication
  %\vspace{10mm}
  \vfill
]
